Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2024-02-19 paper/main.tex
checking in changes to merge upstream

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage[sort&compress, numbers]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}

@@

@@

We fetched these automated transcripts using the
\texttt{youtube-transcript-api} Python package~\citep{Depo18}. The transcripts
consisted of one timestamped line of text for every few seconds (mean: 2.34~s;
standard deviation: 0.83~s) of spoken content in the video (i.e., corresponding
to each individual caption that would appear on-screen if viewing the lecture
via YouTube, and when those lines would appear). We defined a sliding window
length of (up to) $w = 30$ transcript lines, and assigned each window a
timestamp corresponding to the midpoint between the timestamps for its first
and last lines. This $w$ parameter was chosen to match the same number of words
per sliding window (rounded to the nearest whole word, and before
preprocessing) as the sliding windows we defined in our prior
work~\citep{HeusEtal21} (i.e., 185 words per sliding window).

@@

>>>>

\documentclass[10pt]{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage[sort&compress, numbers]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}

@@

\setcitestyle{notesep={; }}

@@

We fetched these automated transcripts using the
\texttt{youtube-transcript-api} Python package~\citep{Depo18}. The transcripts
consisted of one timestamped line of text for every few seconds (mean: 2.34~s;
standard deviation: 0.83~s) of spoken content in the video (i.e., corresponding
to each individual caption that would appear on-screen if viewing the lecture
via YouTube, and when those lines would appear). We defined a sliding window
length of (up to) $w = 30$ transcript lines, and assigned each window a
timestamp corresponding to the midpoint between the timestamps for its first
and last lines. This $w$ parameter was chosen to match the same number of words
per sliding window (rounded to the nearest whole word, and before
preprocessing) as the sliding windows we defined in our prior
work~\citep[][i.e., 185 words per sliding window]{HeusEtal21}.

@@

In the set of analyses reported in Figure~\ref{fig:predictions}, we applied Equation~\ref{eqn:prop} to

estimate participants' knowledge for individual held-out quiz questions (i.e., treating

In the set of analyses reported in Figure~\ref{fig:predictions}, we applied Equation~\ref{eqn:prop} to estimate participants' knowledge at the embedding coordinates of individual held-out quiz questions. For each of the three quizzes a participant took,

Equation~\ref{eqn:prop} to estimate participants' knowledge at the embedding coordinate of individual held-out questions, based on other questions

all other questions (``All questions''; Fig.~\ref{fig:predictions}, top row),

(``All questions''; Fig.~\ref{fig:predictions}, top row).
This test was intended to assess the overall predictive power of our approach. 
Second, we estimated knowledge for each question about a given lecture using only the other questions (from the same participant and quiz) about that \textit{same} lecture (``Within-lecture''; Fig.~\ref{fig:predictions}, middle rows). 
This test was intended to assess the \textit{specificity} of our approach by asking whether our predictions could distinguish between questions about different content covered by the same lecture.
Third, we estimated knowledge for each question about one lecture using only questions (from the same participant and quiz) about the \textit{other} lecture (``Across-lecture''; Fig.~\ref{fig:predictions}, bottom rows).

To analyze the predictive value of

To predict individual participants' success on held-out quiz questions, we used Equation~\ref{eqn:prop}

$$
    \mathtt{accuracy \sim knowledge + (knowledge\ \vert\ participant) + (knowledge\ \vert\ question)}
$$

%\begin{lstlisting}[language=R]
%    accuracy \sim knowledge + (knowledge|participant) + (knowledge|question)
%\end{lstlisting}

note that qID is implicitly nested within levels of lecture
